### 2022-04-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@f3162065c1002a2b64bc983127ad9961ce2932c0 🚀

For all bat hosts of betacoronaviruses, we extracted their predicted
viral sharing network (Albery et al.~2020). This network stores pairwise
values of viral community similarity. To project viral sharing values
into a single value for every pixel, we averaged the pairwise scores.
High values of the average sharing propensity means that this specific
extant bat assemblage is likely to be proficient at exchanging viruses.

@@

To visualize the aggregated risk at the global scale, we combine the
three individual risk components (phylogenetic diversity, compositional
uniqueness, and viral sharing) using an additive color model (Seekell et
al.~2018). In this approach, every risk component gets assigned a
component in the RGB color model (phylogenetic diversity is green,
compositional uniqueness is red, and viral sharing is blue). In order to
achieve a valid RGB measure, all components are re-scaled to the
{[}0,1{]} interval. This additive model conveys both the intensity of
the overall risk, but also the nature of the risk as colors diverge
towards combinations of values for three risk components.

@@

@@

@@

@@

>>>>

For all bat hosts of betacoronaviruses, we extracted their predicted
viral sharing network (Albery et al. 2020). This network stores pairwise
values of viral community similarity. To project viral sharing values
into a single value for every pixel, we averaged the pairwise scores.
High values of the average sharing propensity means that this specific
extant bat assemblage is likely to be proficient at exchanging viruses.

@@

To visualize the aggregated risk at the global scale, we combine the
three individual risk components (phylogenetic diversity, compositional
uniqueness, and viral sharing) using an additive color model (Seekell et
al. 2018). In this approach, every risk component gets assigned a
component in the RGB color model (phylogenetic diversity is green,
compositional uniqueness is red, and viral sharing is blue). In order to
achieve a valid RGB measure, all components are re-scaled to the
{[}0,1{]} interval, so that a pixel with no sharing, no phylogenetic
diversity, and no compositional uniqueness is black, and a pixel with
maximal values for each is white. This additive model conveys both the
intensity of the overall risk, but also the nature of the risk as colors
diverge towards combinations of values for three risk components. Out of
the possible combinations, the most risky in terms or rapid
diversification and spillover potential is high phylogenetic diversity
and low viral sharing (Gomulkiewicz et al. 2000, Cavender-Bares et al.
2009), in that this allows multiple independent host-virus
coevolutionary dynamics to take place in the same location. In the
colorimetric space, this correspond to yellow -- because the HSV space
is more amenable to calculations for feature extraction (see \emph{e.g.}
Keke et al. 2010), we measured the risk level by calculating the angular
distance of the hue of each pixel to a reference value of 60, and
weighted this risk level by the value component. Specifically, given a
pixel with colorimetric coordinates \((h,s,v)\), its ranged weighted
risk value is

\[
v\times\left[1-\frac{\left|\text{atan}\left(\text{cos}(\text{rad}(h)), \text{sin}(\text{rad}(h))\right) - X\right)\right|}{2\pi}\right]\,,
\]

where X is \(atan(cos(deg2rad(60.0)), sin(deg2rad(60.0))\), a constant
approximately equal to \(0.5235\).

@@

\leavevmode\hypertarget{ref-Cavender-Bares2009MerCom}{}%
Cavender-Bares, J. et al. 2009. The merging of community ecology and
phylogenetic biology. - Ecol. Lett. 12: 693--715.

@@

\leavevmode\hypertarget{ref-Gomulkiewicz2000HotSpo}{}%
Gomulkiewicz, R. et al. 2000. Hot Spots, Cold Spots, and the Geographic
Mosaic Theory of Coevolution. - The American Naturalist 156: 156--174.

@@

\leavevmode\hypertarget{ref-Keke2010StuSki}{}%
Keke, S. et al. 2010. Study on skin color image segmentation used by
Fuzzy-c-means arithmetic. - 2010 Seventh International Conference on
Fuzzy Systems and Knowledge Discovery 2: 612--615.

@@

\leavevmode\hypertarget{ref-Seekell2018GeoLak}{}%
Seekell, D. A. et al. 2018. A geography of lake carbon cycling. -
Limnology and Oceanography Letters 3: 49--56.
